Efficient toolkit implementing best practices for principal component analysis of population genetic data

### 2019-10-17 paper-bedpca.tex
save

>>>>

% latex table generated in R 3.5.2 by xtable 1.8-4 package
% Thu Oct 17 16:12:09 2019
\begin{table}[ht]
\centering
\caption{Reported ancestry (left) of POPRES individuals and their matching to 1000G populations (top) by our method. See the description of 1000G populations at \url{https://www.internationalgenome.org/category/population/}.} 
\label{tab:ancestry-pred-popres}
\begin{tabular}{|l|c|c|c|c|c|c|}
  \hline
 & EUR\_CEU & EUR\_FIN & EUR\_GBR & EUR\_IBS & EUR\_TSI & NA \\ 
  \hline
Anglo-Irish Isles & 109 &  & 108 &  &  & 49 \\ 
  Belgium & 25 &  & 4 &  &  & 14 \\ 
  Central Europe & 5 &  &  &  & 1 & 49 \\ 
  Eastern Europe & 1 &  &  &  &  & 29 \\ 
  France & 13 &  &  & 14 &  & 62 \\ 
  Germany & 31 &  & 3 &  &  & 37 \\ 
  Italy &  &  &  & 13 & 19 & 187 \\ 
  Netherlands & 12 &  & 1 &  &  & 4 \\ 
  Scandinavia & 3 & 1 &  &  &  & 11 \\ 
  SE Europe &  &  &  &  & 6 & 88 \\ 
  SW Europe &  &  &  & 211 &  & 53 \\ 
  Switzerland & 29 &  & 4 & 7 &  & 182 \\ 
   \hline
\end{tabular}
\end{table}
